Risk Perceptions for Wearable Devices

### 2015-03-04 tex-inputs/discussion.tex
paper cleanup
tweaks to discussion section

\subsection{Interpreting the Survey Results}
One of the main limitations of this work is that our participants might not have interest in or knowledge of wearables and their capabilities. 83\% of our participants reported that they do not own a wearable device. These participants may have underestimated or overestimated the risk perceived in various scenarios. People may be overreacting to recent events for scenarios \footnote{During our study, there were many stories covering injuries from exploding batteries (http://www.bloomberg.com/news/articles/2014-08-11/exploding-lithium-batteries-riskier-to-planes-research), which were explicitly and repeated mentioned when self-reporting concerns.}. People may be underestimating the risk of sharing certain data due to unawareness of what can be inferred from the data, or not have an idea of how to rate a new technology with respect to familiar ones. Biometrics were generally not a concern for our participants, although there are many security and privacy implications \cite{prabhakar2003biometric}. {\color {red} Any economics or behavioral papers to support our claims and elaborate on this would be great here. Maybe ones on perception, estimation, etc.}

@@

Privacy concerns asked out of context differ from how users may react to these same concerns in real life. This is an unavoidable, yet important consideration of any study of this nature. This privacy paradox means that our findings may not be exactly representative of how upset users may be in real life, but do reflect their perceptions of wearable devices and various associated scenarios.

>>>>

\subsection{Interpreting the Survey Results}
One of the main limitations of this work is that our participants might not have interest in or knowledge of wearables and their capabilities. 83\% of our participants reported that they do not own a wearable device. These participants may have underestimated or overestimated the risk perceived in various scenarios. People may be overreacting to recent events for scenarios \footnote{During our study, there were many stories covering injuries from exploding batteries (http://www.bloomberg.com/news/articles/2014-08-11/exploding-lithium-batteries-riskier-to-planes-research), which were explicitly and repeated mentioned when self-reporting concerns.}. People may be underestimating the risk of sharing certain data due to unawareness of what can be inferred from the data, or not have an idea of how to rate a new technology with respect to familiar ones. Biometrics were generally not a concern for our participants, although there are many security and privacy implications \cite{prabhakar2003biometric}.

@@

Privacy concerns asked out of context differ from how users may react to these same concerns in real life \cite{norberg2007privacy, jensen2005privacy}. This is an unavoidable, yet important consideration of any study of this nature. This privacy paradox means that our findings may not be exactly representative of how upset users may be in real life, but do reflect their perceptions of wearable devices and various associated scenarios.
